\section{Impossibility}\label{sec:impossibility}

We saw that in the synchronous setting and in the partially synchronous setting after GST,
protocols can be timely.
Conversely, in the following theorem, we show that timeliness before GST in partially
synchronous networks is unachievable.

\begin{theorem}[Timeliness is Impossible in Partial Synchrony]
  In a partially synchronous communication network, a distributed temporal ledger protocol
  which is safe and live$(u)$, cannot be timely at all times.
\end{theorem}
\begin{proof}
  Suppose, towards a contradiction, there is a safe, live$(u)$, and timely$(v)$ distributed temporal ledger protocol.
  There is a fixed number of $n$ parties.
  Consider the following two worlds:

  \noindent
  \underline{World A}
  There are $n-1$ honest parties and one adversarial party. The adversary remains silent and
  does not disrupt the synchrony of the network ($\gst = 0$).
  The adversary chooses any round $r$ and introduces a high entropy transaction $\tx$ to the honest parties. We are in
  synchrony, hence, because of liveness, $\tx$ appears in the ledgers of all honest parties
  by round $r + u$. The transaction is recorded with round $r^* \leq r + u$ because of
  timeliness requirement \ref{def:timely-past}.

  \noindent
  \underline{World B}
  All parties are honest. We are under partial synchrony, and the adversary partitions the network such that
  one honest party $P$ is isolated from the other $n-1$ honest parties.
  The adversary sets \gst to  $r + u + v + 1$.
  Before \gst, at round $r$, the transaction $\tx$ is introduced to the $n-1$ connected
  honest parties. In the view of these parties,
  World A and World B are identical up to now. Hence, like in World A,
  they report $\tx$ in their ledgers by round $r + u$, with recorded round $r^* \leq r + u$.

  Only after \gst, due to liveness, will the transaction eventually be included in $P$'s ledger.
  Consider the earliest round $r_2$, when $\tx$ appears in the ledger.
  The transaction will have recorded round $r^*$, due to safety.
  Hence, $(r^*, \tx) \in \Ledger[][P][r_2][|\Ledger[][P][\gst - 1]|:]$.
  From timeliness requirement \ref{def:timely-chunk}, we
  get $r^* > \gst - v - 1$. Therefore, $r^* > r + u$.
  This is a contradiction, since $r^* \leq r + u$.
  \atnote{Maybe write this last part a bit better?}
  \Qed
\end{proof}
