\subsection{Streamlet is Timely}

We now prove that the Partially Synchronous Streamlet Protocol is timely,
in the partially synchronous setting, after GST.
We work in the same model as the Streamlet paper~\cite{streamlet},
in particular assuming a PKI.

First, we turn Streamlet into a temporal blockchain protocol.
\emph{Temporal Streamlet} is the Streamlet protocol with the
following additions: No future epoch blocks are accepted. In each block, we report
$2\Delta e$ as the recorded round, where $e$ is its epoch.
Temporal Streamlet remains safe ---in their language \emph{consistent}--- and live($u$)
for $\frac{t}{n} < \frac{1}{3}$. Furthermore, it has consistent recorded rounds.

Honest party $P$, at the beginning of round $r$, and
before performing any other action, checks the network and
stores the longest finalized chain $\chain^P_r$.
Let $G(e)$ be the predicate indicating that epochs $e-3,e-2,e-1,e,e+1$ have honest leaders.
Before proving freshness, we first show the maximum interval between two consecutive fully
honest epoch quintuples is bounded.

\begin{definition}[Temporal Streamlet Typical Execution]
  Consider an execution of the Temporal Streamlet protocol with duration
  of $E$ epochs, $n$ total number of parties and $t$ number of corrupt parties.
  Let $J = \{0,E\} \cup \{0 < e < E: G(e)\}$.
  The execution is \emph{typical} if for all
  $d \geq \frac{\kappa + \lg \floor*{\frac{E}{5}}}{- \lg \left(1 - \left(\frac{n - t}{n}\right)^5\right)}$:
  $\max_{e \in J}(\min_{\substack{e' > e \\ e' \in J}}(e' - e)) \leq d$.
\end{definition}

\begin{lemma}[Temporal Streamlet Typicality] \label{lem:honest-quintuple}
  A Temporal Streamlet execution is typical, except with negligible probability in $\kappa$.
\end{lemma}
\begin{proof}
  We let $K = \{0, E\} \cup \{e \in \{0, 5, 10 ,\ldots, 5\floor*{\frac{E}{5}}\}: G(e)\}$.
  It holds that
  $\max_{e \in J}(\min_{\substack{e' > e \\ e' \in J}}(e' - e)) \leq \max_{e \in K}(\min_{\substack{e' > e \\ e' \in K}}(e' - e))$.
  Therefore:

  \begin{gather*}
      \Pr [\max_{e \in J}(\min_{\substack{e' > e \\ e' \in J}}(e' - e)) > d] \leq \\
      \Pr [\max_{e \in K}(\min_{\substack{e' > e \\ e' \in K}}(e' - e)) > d] \leq \\
      \floor*{\frac{E}{5}} \left(1 - \left(\frac{n - t}{n}\right)^5\right)^d
  \end{gather*}

  For the second inequality, we observe that each chunk is a Bernoulli trial and we
  apply a union bound.
  Letting $F = \left(1 - \left(\frac{n - t}{n}\right)^5\right)$, we obtain
  $\floor*{\frac{E}{5}} F^d \leq 2^{-\kappa} \Rightarrow
   d \lg F \leq -\kappa - \lg \floor*{\frac{E}{5}} \Rightarrow
   d \geq \frac{\kappa + \lg \floor*{\frac{E}{5}}}{- \lg F}
  $.
  \Qed
\end{proof}

\begin{lemma}[Temporal Streamlet Freshness] \label{lem:latest-finalized-round}
  Temporal Streamlet is fresh($2\Delta d$).
\end{lemma}
\begin{proof}
  Let $r$ be the current round of the current epoch $e$
  and $r^*,e^*$ be the recorded round and, respectively, epoch of the tip
  of an honest party's finalized chain.
  Let $e' = \max(\{\hat e \leq e: G(\hat e)\} \cup \{0\})$.
  From typicality, it holds that $e - e' \leq d$.
  From the proof of Streamlet liveness~\cite[Theorem 6]{streamlet}, epoch $e'$ contains a finalized
  block. This block cannot be after the tip.
  Hence, $e' \leq e^*$. Therefore, $e - e^* \leq d \Rightarrow r - r^* \leq 2\Delta d$.
  \Qed
\end{proof}

From the above and Theorem~\ref{thm:freshness-to-timeliness}, it follows that
Temporal Streamlet is timely($2\Delta d$).
